---
title: "Predicting footfall as per the temperature"
output: html_notebook
---
#importing fpp,fpp2,TTR packages
```{r message=FALSE}
library(fpp)
library(fpp2)
library(TTR)
```

#Name of the data
```{r}
Final 
```

#plotting a time series graph, summary and boxplot 
```{r}
t1<- ts(Final$footfalls,frequency=52, start= c(2011,09))
plot(t1, main="Time series plot")
summary(t1)
boxplot(t1, main="Boxplot of Time Series")
Acf(t1)
```

#Decomposition of the time series
```{r}
decomp <- stl(t1,s.window ="periodic")
plot(decomp)
```

#seasonally adjusting the time series 

# A seasonally adjusted value removes the seasonal effect from a value so that trend can be seen more clearly 
```{r}
decomp_sesadj <- seasadj(decomp)
decomp1<- stl(decomp_sesadj, s.window ="periodic")
plot(decomp1)
```

#plot of time series and decomp adjusted for seasonality 
```{r}
plot(t1)
lines(decomp_sesadj,col="Red")
```

##1. Mean forecast
```{r}
mean_forecast <- meanf(t1,5)
mean_forecast
plot(mean_forecast)
```

#Taking the residuals of mean_forecast and plotting the Acf 
```{r}
r<-mean_forecast$residuals
Acf(r)
```

# Cheching the ACCURACY 
```{r}
accuracy(mean_forecast)
```

##2. Naive 
# Naive is a simple algorithm. it may or may not solve the problem but it provides the benchmark for all other models 
# Naive model simply takes the last observed value and predicts it for the future (903 in our case)
#plotting naive model and attributes of naive model 

```{r}
naive_forecast <- naive(t1)
attributes(naive_forecast)
naive_forecast
plot(naive_forecast)
```

# Taking the residuals of naive_forecast and plotting the Acf 

```{r}
plot(naive_forecast$residuals)
Acf(naive_forecast$residuals) #does not show spike at lag 0 and starts from lag 1
```

#plotting the histogram 
```{r}
hist(naive_forecast$residuals)
```

# plotting fitted vs residual of naive
# it is used to detech outliers, error variance, and non linearity 
```{r}
plot(naive_forecast$fitted,naive_forecast$residuals,xy.labels= FALSE,xy.lines = FALSE)
```

#measuring the accuracy
```{r}
accuracy(naive_forecast)
## MAPE = 11.15
```

##3. SNAIVE MODEL
# plotting snaive model and attributes of snaive model 
```{r}
snaive_forecast<- snaive(t1, h=4)
snaive_forecast
plot(snaive_forecast)
lines(snaive_forecast$mean,col="pink")
lines(snaive_forecast$fitted,col="purple")
```

#Acf and residuals, histogram
```{r}
Acf(snaive_forecast$residuals)  # shows if the points are co-related 
plot(snaive_forecast$residuals)
hist(snaive_forecast$residuals)
plot(snaive_forecast$fitted,snaive_forecast$residuals,xy.labels= FALSE,xy.lines = FALSE, main="Residual Plot")
```

#Accuracy for snaive forecast
```{r}
accuracy(snaive_forecast)
```

##4. Moving Average model
```{r}
MA3 <- ma(t1,order=3)
MA6 <- ma(t1,order=6)
MA9 <- ma(t1,order=9)
plot(MA3, col="Red", main="Graph of Moving average with order 3")
plot(MA6, col="Blue", main="Graph of Moving average with order 6")
plot(MA9, col="Green", main="Graph of Moving average with order 9")
plot(t1, main="Graph of Time series graph with Moving avg plot with order 3,6,9")
lines(MA3, col='Red')
lines(MA6, col='Blue')
lines(MA9, col='Green')
```

#Forecast using MA and its accuracy
```{r}
MA3_forecast <- forecast(MA3, h=4)
MA3_forecast
plot(MA3_forecast,col= "Red", main="Graph of time series with moving average forecast with order 3")
lines(t1)
accuracy(MA3_forecast)
MA6_forecast <- forecast(MA6, h=4)
MA6_forecast
plot(MA6_forecast,col= "Blue", main="Graph of time series with moving average forecast with order 6")
lines(t1)
accuracy(MA6_forecast)
MA9_forecast <- forecast(MA9, h=4)
MA9_forecast
plot(MA9_forecast,col= "Green", main="Graph of time series with moving average forecast with order 9")
lines(t1)
accuracy(MA9_forecast)
```



##5. Holtswinter method
```{r}
t1_hw <- HoltWinters(t1)
t1_hw
```

#attibutes of Holtswinter
```{r}
attributes(t1_hw)
t1_hw$SSE
t1_hw$coefficients
```

#forecast with Holtswinter, Acf plot
```{r}
forecast_hw <- forecast(t1_hw,h=5)
forecast_hw
plot(forecast_hw)

```

#Accuracy of Holtswinter
```{r}
accuracy(forecast_hw)
```

##6. Auto Arima
```{r}
adf.test(t1)
kpss.test(t1)
nsdiffs(t1)
tsdisplay(t1)
auto.arima(t1)
# use this in the exam stepwise=false and trace=true
arima_model<- auto.arima(t1, trace=TRUE, stepwise=FALSE)
```

#forecast using Arima and its accuracy
```{r}
arima_forecast<- forecast(arima_model)
arima_forecast
accuracy(arima_forecast)
```

##7. Linear Regression
```{r message=FALSE}
library(UsingR)
model <- lm(Final$footfalls~Final$air_temp)
summary(model)
plot(Final$footfalls,Final$air_temp,pch=19, col="blue", main="Scatter Plot")
```
#correlation check
```{r}
model1<- cor(Final$footfalls,Final$air_temp)
model1
```

#Plotting the model
```{r}
plot(Final$footfalls~Final$air_temp, pch=19, col="blue", main="Scatter Plot with R2 value" )
abline(lm(Final$footfalls~Final$air_temp), col="red")
legend("topright", bty="n", legend=paste("R2 is", format(summary(model)$adj.r.squared, digits=4)))
#lines(model$fitted.values, col="Red")
#plot(model$residuals, model$fitted.values)

```

